\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Thanakrit Jomhong} \\ \vspace{1pt}
    \small 092-275-1575 $|$ \href{mailto:thanakritjomhong@gmail.com}{\underline{thanakritjomhong@gmail.com}} $|$
    \href{https://www.linkedin.com/in/thanakrit-jomhong-8b600034b}{\underline{linkedin}} $|$
    \href{https://github.com/northlnwza}{\underline{github}}
\end{center}

\section{Profile}
\small I am a Computer Engineering student driven by curiosity, mastery, and clarity. I thrive on solving problems, learning deeply, and helping others see what I see. I enjoy connecting ideas across disciplines and turning complexity into structure. My long-term goal is to build meaningful systems that create real world impact.

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Mahidol University}{Aug. 2024 -- May 2028}
      {Bachelor of Engineering Program in Computer Engineering}{GPA 3.96}
    \resumeSubheading
      {Suksanareewittaya School}{May 2021 -- Mar. 2024}
      {High School, Computer STEM Program}{GPA 4.00}
    \resumeSubheading
      {English Score}{}
      {MU-ELT 113/150 (Equivalent to TOEIC 850+)}{}
  \resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages \& Databases}{: Python, C, C++, JAVA, SQL, HTML / CSS} \\
    \textbf{Libraries \& Frameworks}{: Pandas, Numpy, Matplotlib, Seaborn, PyTorch, Scikit-learn} \\
    \textbf{Tools}{: Git, Github, Supabase, Vercel, Google Colab, VS Code, spreadsheet, MATLAB, n8n, Docker}
  }}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Head of Sponsorship Coordinator | ClickCamp16, Mahidol Computer Engineering}{May 2025 -- Dec. 2025}{}{}
    \resumeItemListStart
      \resumeItem{Negotiation \& Relationship Management}
      \resumeItem{Formal Contact over 200+ company, apply data management skills}
      \resumeItem{Secured [130,000] THB in funding}
    \resumeItemListEnd

  \resumeSubheading
    {Piscine 42Bangkok School | 42school, KMITL}{May 2024 -- Jun. 2024}{}{}
    \resumeItemListStart
      \resumeItem{Completed the one-month selection program at 42}
      \resumeItem{Trained 70 -100 hours per week, developing autonomy, adaptability, and collaboration skills while building multiple projects under real deadlines.}
      \resumeItem{Relevant Coursework : UNIX \& Shell, Git \& Version Control, C Programming}
    \resumeItemListEnd

  \resumeSubheading
    {Talent Robotics, AI and Coding (Talent RAC) | AI Track, Sirindhorn Science Home}{Oct. 2023}{}{}
    \resumeItemListStart
      \resumeItem{A program by IPST, and NECTEC aimed to develop future talents in robotics, AI, and coding through online and on-site training, and hands-on projects from real-world industry.}
      \resumeItem{Completed onsite training in AI application, 3D design, and IOT}
      \resumeItem{Designed and implemented an security check system utilizing sensors and image classification model by kidbrightmicroAI platform}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
      {\textbf{HR-ChatBot} $|$ \emph{n8n, Docker, PosrtgresSQL (Supabase), LLM and RAG}}{}
      \resumeItemListStart
        \resumeItem{Developed a cross-platform chatbot to automate HR workflows like leave requests and benefit inquiries through the LINE Messaging API}
        \resumeItem{Integrated LLM to achieve high-accuracy natural language intent extraction}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{BananaRipnessClassification} $|$ \emph{Python, PyTorch and scikit-learn}}{}
      \resumeItemListStart
        \resumeItem{Developed a Deep Learning image classification model using ResNet34 and Fastai to identify banana varieties and ripeness stages with F1-score of 87.5\% on the test set.}
        \resumeItem{Optimized model performance through transfer learning and learning rate scheduling, significantly reducing manual inspection time for agricultural quality assessment.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Bangkok Public Transportation Passenger Insights} $|$ \emph{Pandas, NumPy, Scipy, Plotly, Seaborn, Matplotlib}}{}
      \resumeItemListStart
        \resumeItem{Analyzed 14 months of multi-modal transit data (BTS, MRT, ARL, Red Line Train) to identify passenger growth trends, market share shifts, and service stability}
        \resumeItem{Developed a Z-Score anomaly detection model to correlate passenger volume fluctuations with 35+ specific Thai holidays and events}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Extracurricular Activities \& Awards}
\resumeSubHeadingListStart
  \resumeProjectHeading
      {\textbf{16th Jitasa Camp, Mahidol Engineering Volunteer Club}}{Dec. 2025}
  \resumeProjectHeading
      {\textbf{2nd Place Winner, Practice AI, Super AI Engineer SS5 (AI INOVATOR TRACK, Western Region)}}{Summer 2025}
  \resumeProjectHeading
      {\textbf{STAFF Group Leader, CTFriends2, Mahidol Engineering Cybersecurity Club}}{Apr. 2025}
  \resumeProjectHeading
      {\textbf{STAFF Tickets Seller, INCRISIS Concert, Mahidol Engineering Student Association}}{Apr. 2025}
  \resumeProjectHeading
      {\textbf{Participate in Invent for the planet Hackathon, INT Mahidol}}{Feb. 2025}
  \resumeProjectHeading
      {\textbf{STAFF Entertainment \& Group Leader, ClickCamp15, Mahidol Computer Engineering}}{Dec. 2024}
  \resumeProjectHeading
      {\textbf{Gold Medal, Onsite presentation, Data Science Project Contest 2023, CMU}}{Sep. 2023}
\resumeSubHeadingListEnd

\end{document}
